---
title: "R Notebook"
output: 
   html_document:
    toc: true
    toc_float: true
    df_print: paged
bibliography: bioinfo.bib
---

This workflow is for using [Sourcetracker (v1)](https://github.com/danknights/sourcetracker) with phyloseq formatted objects. Download the sourcetracker script before beginning.

The otu and tax tables have been saved as .csv files. 

For more on sourcetracker [see @knights2011]

# Set Up

```{r, results='hide', message=FALSE, warning=FALSE}

library(ape)
library(plyr)
library(dplyr)
library(ggplot2)
library(gplots)
library(lme4)
library(tidyr)
library(vegan)
library(scales)
library(grid)
library(reshape2)

library(gridExtra)

m.g.colors <- c( "#999999", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#CBD588", "#5F7FC7", "orange","#DA5724", "#508578", "#CD9BCD",
   "#AD6F3B", "#673770","#D14285", "#652926", "#C84248", 
  "#8569D5", "#5E738F","#D1A33D", "#8A7C64", "#599861" )

more.colors <- c("indianred1", "steelblue3",  "skyblue1", "mediumorchid","royalblue4", "olivedrab3",
   "pink", "#FFED6F", "mediumorchid3", "ivory2", "tan1", "aquamarine3", "#C0C0C0",
    "mediumvioletred", "#999933", "#666699", "#CC9933", "#006666", "#3399FF",
   "#993300", "#CCCC99", "#666666", "#FFCC66", "#6699CC", "#663366", "#9999CC", "#CCCCCC",
   "#669999", "#CCCC66", "#CC6600", "#9999FF", "#0066CC", "#99CCCC", "#999999", "#FFCC00",
   "#009999", "#FF9900", "#999966", "#66CCCC", "#339966", "#CCCC33", "#EDEDED"
)

theme_set(theme_classic(base_size=12, base_family="Avenir"))
```

Read in the OTU table

```{r}
otu.table <- read.csv("TwoHarbors_OTU_table", row.names=1)
otu.table
```

Read metadata file. I added a column named SourceSink (in excel) that labels each sample as either a source or a sink. You could also easily do this in R.

```{r}
metadata = read.csv("TwoHarbors_seq_metadata2.csv", header=TRUE, row.names=1)
metadata
```

In this dataset, the most upstream site is site9 (skunk creek transition or skunk creek upstream)
skunk creek tributary is upstream
(below a retention pond)

other skunk creek sites are downstream. most downstream is burlington bay

agate bay:
both storm water outfall and wastewater outfall can be sources
beach is most downstream



***Sourcetracker wants the sample names as rows in an otu table and the metadatafile, which is the opposite of how phyloseq likes it.***


To make this run faster the first time, let's just look at families and rarefy to even depth using a quick scaling function


```{r}
library(phyloseq)
tax.table <- read.csv("TwoHarbors_tax_table", header=TRUE, row.names=1)

# This just scales the otu counts to the lowest depth in the table. You should use the bootstrapped version if you have it.
mindepth <- min(colSums(otu.table))
s.otu.table <- data.frame(apply(otu.table, 2, function(x) round(x*mindepth/sum(x))))

#Replace single values with 0
s.otu.table[s.otu.table==1] <- 0

#Drop OTUs that are now all zeros
s.otu.table <- s.otu.table[which(rowSums(s.otu.table)>0),]

#Assemble phyloseq!
mothur.data <- merge_phyloseq(otu_table(s.otu.table, taxa_are_rows=TRUE), tax_table(as.matrix(tax.table)), sample_data(metadata))

mothur.data

#To work with most public datasets of source, you'll need to agglomerate OTUs into some taxonomic rank. I tried with families and genera.
family.glom <- tax_glom(mothur.data, taxrank="Family")

genus.glom <- tax_glom(mothur.data, taxrank="Genus")


#Break apart the phyloseq object into agate bay and skunk creek only
ab.physeq <- prune_samples(sample_data(family.glom)$watershed == "Agate Bay", family.glom) %>% prune_taxa(taxa_sums(.) > 0,.)

sc.physeq <- prune_samples(sample_data(family.glom)$watershed == "Skunk Creek", family.glom)%>% prune_taxa(taxa_sums(.) > 0,.)

ab.physeq
sc.physeq

#make OTU tables
ab.family.otus <- data.frame(otu_table(ab.physeq))
sc.family.otus <- data.frame(otu_table(sc.physeq))

#make metadata files that only have sc/ab samples.
sc.metadata <- data.frame(sample_data(sc.physeq))
ab.metadata <- data.frame(sample_data(ab.physeq))
```


# Skunk Creek 

orientation fix from phyloseq style to sourcetracker style
```{r}
t.otus <- t(as.matrix(sc.family.otus))
```


Find indices of source and sink samples and put their category type in the variable called 'envs.'
```{r}
train.ix <- which(sc.metadata$SourceSink=='source')
test.ix <- which(sc.metadata$SourceSink=='sink')
envs <- sc.metadata$Site_location

desc <- sc.metadata$Site_location

```

Change this line to reflect wherever you downloaded sourcetracker to
```{r}
source('/volumes/dean/chunlab/sourcetracker/src/SourceTracker.r')
```


tune the alpha values using cross-validation (this is slow! like very slow!) Use 0.001 if pressed for time.
```{r, eval=FALSE}
tune.results <- tune.st(t.otus[train.ix,], envs[train.ix])
alpha1 <- tune.results$best.alpha1
alpha2 <- tune.results$best.alpha2

alpha1
alpha2
```

```{r, include=FALSE}
alpha1 <- 0.001
alpha2 <- 0.001
```


Train sourcetracker using the source samples.  Be unafraid of an error message that says 'the condition has length > 1 and only the first element will be used.' Seems to be an internal bug that doesn't affect the outcome.

```{r}
st <- sourcetracker(t.otus[train.ix,], envs[train.ix])
```

Estimate source proportions in sink samples.
```{r}
results <- predict(st,t.otus[test.ix,], alpha1=alpha1, alpha2=alpha2)
```

This part validates the models we made using the original training data.
```{r}
results.train <- predict(st, alpha1=alpha1, alpha2=alpha2)
```


Here are some (really ugly) pie charts that sourcetracker will plot for you. You can also try type = 'bar' or 'dist' though I think really those outputs are not easily customizable.
```{r}
# plot results
labels <- desc
plot(results, labels[test.ix], type='pie')
```

```{r}
# plot results with legend
plot(results, labels[test.ix], type='pie', include.legend=TRUE)
plot(results.train, labels[train.ix], type='pie', include.legend=TRUE)
```

Instead of using those plots, you can extract the results like so and then make all your plots in either base R or ggplot just like you've already learned to do.

```{r}
downstream <- data.frame(results$proportions)
downstream$id <- row.names(downstream)
meltdown <- melt(downstream, id.vars=c("id"))

sc.metadata 

colnames(meltdown) <- c("id", "Upstream.Site", "Proportion")
meltdown$Downstream.Site <- sc.metadata[as.vector(meltdown$id), "Site_location"]
meltdown$Date <- sc.metadata[as.vector(meltdown$id), "Date_sampled"]
meltdown$Category <- sc.metadata[as.vector(meltdown$id), "sampling_category"]

#Some manipulation here to create more variables. You can also do this in excel with your original metadata file before you start any of this if you'd rather. 
meltdown$Month <- sapply(meltdown$Date, function(x) strsplit(x, "/")[[1]][1])
meltdown
```

```{r}
theme_set(theme_classic(base_size=10, base_family="Avenir"))

ggplot(meltdown, aes(x=id, y=Proportion, fill=Upstream.Site)) + geom_bar(stat="identity") + facet_wrap(~Downstream.Site+Month, scales="free") + theme(axis.text.x = element_blank()) + scale_fill_manual(values=m.g.colors, name="Source Sites", labels=c("Skunk Creek Transition", "Skunk Creek Tributary", "Unknown")) + xlab("")
```

Save a high quality version.

```{r, eval=FALSE}
ggsave("skunkcreek_family_example_fwrap.png", width=7, height=5, dpi=300)
```


# Genus Skunk Creek

This is the same analysis as above but with Genera rather than family and some fancier plotting at the end.

```{r}
sc.physeq <- prune_samples(sample_data(genus.glom)$watershed == "Skunk Creek", genus.glom)%>% prune_taxa(taxa_sums(.) > 0,.)

sc.physeq

sc.gen.otus <- data.frame(otu_table(sc.physeq))

sc.metadata <- data.frame(sample_data(sc.physeq))
```

```{r}
t.otus <- t(as.matrix(sc.gen.otus))
train.ix <- which(sc.metadata$SourceSink=='source')
test.ix <- which(sc.metadata$SourceSink=='sink')
envs <- sc.metadata$Site_location

desc <- sc.metadata$Site_location

```

```{r, eval=FALSE}
tune.results <- tune.st(t.otus[train.ix,], envs[train.ix])
alpha1 <- tune.results$best.alpha1
alpha2 <- tune.results$best.alpha2

alpha1
alpha2
```

```{r}
st <- sourcetracker(t.otus[train.ix,], envs[train.ix])
```

Estimate source proportions in test data
```{r}
results <- predict(st,t.otus[test.ix,], alpha1=alpha1, alpha2=alpha2)
```

```{r}
results.train <- predict(st, alpha1=alpha1, alpha2=alpha2)
```

```{r}
downstream <- data.frame(results$proportions)
downstream$id <- row.names(downstream)
meltdown <- melt(downstream, id.vars=c("id"))

sc.metadata 

colnames(meltdown) <- c("id", "Upstream.Site", "Proportion")
meltdown$Downstream.Site <- sc.metadata[as.vector(meltdown$id), "Site_location"]
meltdown$Date <- sc.metadata[as.vector(meltdown$id), "Date_sampled"]
meltdown$Category <- sc.metadata[as.vector(meltdown$id), "sampling_category"]

meltdown$Month <- as.factor(sapply(meltdown$Date, function(x) strsplit(x, "/")[[1]][1]))
levels(meltdown$Month) <- c("June", "July", "August")
meltdown$Day<- as.factor(sapply(meltdown$Date, function(x) strsplit(x, "/")[[1]][2]))

meltdown$Rep <- as.factor(sapply(meltdown$id, function(x) strsplit(x, "_")[[1]][3]))
levels(meltdown$Rep) <- c("A", "AA", "B")

meltdown$Category <- as.factor(meltdown$Category)
levels(meltdown$Category) <- c("B", "E")
 
meltdown$SID <- as.factor(sapply(meltdown$id, function(x) strsplit(x, "_")[[1]][5]))

meltdown$TypeRep <- paste(meltdown$Category, meltdown$Rep, meltdown$Day, sep=".")
```

```{r}
theme_set(theme_classic(base_size=10, base_family="Avenir"))

ggplot(meltdown, aes(x=TypeRep, y=Proportion, fill=Upstream.Site)) + geom_bar(stat="identity") + facet_wrap(~Downstream.Site+Month, scales="free_x") + scale_fill_manual(values=m.g.colors, name="Source Sites", labels=c("Skunk Creek Transition", "Skunk Creek Tributary", "Unknown")) + xlab("")


ggplot(meltdown, aes(x=Category, y=Proportion, fill=Upstream.Site)) + geom_bar(stat="identity") + facet_grid(rows=vars(Downstream.Site), cols=vars(Month), space="free", scales="free_x") + scale_fill_manual(values=m.g.colors, name="Source Sites", labels=c("Skunk Creek Transition", "Skunk Creek Tributary", "Unknown")) + xlab("")
```

```{r, eval=FALSE}
ggsave("skunkcreek_genera_example_fwrap.png", width=9, height=5, dpi=300)
```









